---
title: "Surf Forecast Dashboard"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: fill
    theme: flatly
---

<style>
/* Fond de la page */
body {
    background-color: #f4f7f6;
}

/* Style des cartes (boîtes) */
.chart-wrapper {
    border-radius: 10px; /* Coins arrondis */
    border: none; /* Supprime la bordure standard */
    box-shadow: 0 4px 8px rgba(0,0,0,0.05); /* Ombre légère professionnelle */
    margin-bottom: 20px;
    background: white;
}

/* Style du titre des cartes */
.chart-title {
    font-weight: bold;
    border-bottom: 1px solid #eee;
    padding: 10px 15px;
    color: #2c3e50;
}

/* Navbar personnalisée (couleur surf/océan) */
.navbar {
    background-color: #2c3e50;
    border-bottom: 3px solid #18bc9c;
}

/* Centrer le titre des cadrans */
.chart-title {
    text-align: center;
    font-weight: bold;
    color: #2c3e50;
    width: 100%;
}

</style>

```{r setup, include=FALSE}
library(flexdashboard)
library(reticulate)
library(readr)
library(dplyr)
library(ggplot2)
library(tidyr)
library(knitr)
library(tidyverse)
library(plotly)
library(kableExtra)

# Force R to use your VSCode project's virtual environment
# Move up one level (..) because the Rmd is in 'Partie1' and .venv is above it
use_virtualenv("../.venv", required = TRUE)

# Importation
surf_lib <- import("surf_scrap")

#  Web scraping execution
##Link
URL <- "https://www.surf-report.com/meteo-surf/lacanau-s1043.html"

CSV_OUT <- "data_surf.csv"

# Call the library created on python
surf_lib$scrape_surf_report(URL, output_csv_path = CSV_OUT)

#  Data loading on R
data <- readr::read_csv(CSV_OUT)

# Data cleaning for the KPI computing
df_clean <- data %>%
  # Parse "5.0 - 7.6" into separate values to compute the mean of the range.
  separate(Waves_size, into = c("w_min", "w_max"), sep = " - ", convert = TRUE, remove = FALSE) %>%
  mutate(
    Wave_Mean = (w_min + w_max) / 2,
    Wind_Speed_Num = as.numeric(gsub("[^0-9.]", "", Wind_speed)),
    # Quality Score Calculation (Criteria: wave <1m, wind <50km/h, North direction)
    Is_North = grepl("Nord", Wind_direction),
    Quality_Score = case_when(
      Wave_Mean <= 1.0 & Wind_Speed_Num <= 50 & Is_North ~ 100,
      Wave_Mean <= 2.0 & Wind_Speed_Num <= 60 ~ 60,
      TRUE ~ 30
    ),
    Time_Idx = row_number()
  )

# Identification of the best moments
best_moment <- df_clean %>% arrange(desc(Quality_Score), desc(Wave_Mean)) %>% head(1)
highest_wave <- df_clean %>% arrange(desc(w_max)) %>% head(1)
```


Row {data-height=300}
-----------------------------------------------------------------------

### 🏄 Best moment to pratice surf
```{r}

  valueBox(
  value = paste(best_moment$Day, "@", best_moment$Hour),
  caption = "Best moment to pratice surf",
  icon = "fa-star",
  color = "success"
  )
```


### 📈 Grade of the sea quality

```{r}
#Gauge
gauge(best_moment$Quality_Score, min = 0, max = 100, symbol = '%', gaugeSectors(
  success = c(80, 100), warning = c(40, 79), danger = c(0, 39)
))
```


### 🌊 Highest wave for the week

```{r}
valueBox(
  value = paste(highest_wave$w_max, "m"),
  caption = paste("Forecasted for", highest_wave$Day),
  icon = "fa-arrows-alt-v",
  color = "info"
)
```


Row {data-height=800}
-----------------------------------------------------------------------

### 🌊 Waze size over the time
```{r}

p <- ggplot(df_clean, aes(x = Time_Idx, y = Wave_Mean)) +
  geom_area(fill = "#0077b6", alpha = 0.3) +
  geom_line(color = "#0077b6", linewidth = 1) + 
  theme_minimal() +
  labs(x = "Time", y = "Waze mean(m)")

ggplotly(p) %>% 
  layout(autosize = TRUE, margin = list(l = 0, r = 0, b = 0, t = 40))
```

### 🌬️ Wind speed overthetime
```{r}
p_vent <- ggplot(df_clean, aes(x = Time_Idx, y = Wind_Speed_Num, 
                     text = paste("Hour :", Time_Idx, "<br>Speed :", Wind_Speed_Num, "km/h"))) +
  geom_col(fill = "#90e0ef") +
  theme_minimal() +
  labs(x = "Time", y = "Speed (km/h)")

ggplotly(p_vent) %>% 
  layout(
    autosize = TRUE, 
    margin = list(l = 0, r = 0, b = 0, t = 40, pad = 0)
  )
```

Row {data-height=800}
-----------------------------------------------------------------------

### 📝 Summarise table (day, hour, wave size, wind direction)

```{r}

data %>% 
  select(Day, Hour, Waves_size, Wind_direction) %>% 
  kable(format = "html", align = "c") %>% 
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed", "responsive"),
    full_width = TRUE 
  )
